### 2016-02-04 inputs/materials_and_methods.tex
update in results, discussion
phrasing

In rice, DNA was isolated from three-weeks old leaves using the DNeasy Plant Mini Kit (QIAGEN) with a TECAN Freedom EVO150 liquid handling robot (TECAN Group Ltd, Switzerland). DNA digestion was performed on 100 ng samples in 96-well plates using ApeKI, which was shown to cut every 1 kb on average in a in-silico digestion of the Nipponbare reference genome, and 96-plex libraries constructed according to the GBS protocol. The libraries were loaded into Genome Analyzer II (Illumina, Inc., San Diego, CA) for sequencing. Raw sequence data filtering, sequence alignment to the rice reference genome (Os-Nipponbare-Reference-IRGSP-1.0, \cite{kawahara_improvement_2013}), and SNP calling from GBS genotyping were carried out using the Tassel GBS pipeline \cite{glaubitz_tassel-gbs:_2014}.\\
In total, 32\,706, 40\,734 and 166\,418 SNP markers were called by GBS in Alfalfa-PV, Alfalfa-Med and Rice, respectively (see Table~\ref{tab:descriptive_statistics}). In both datasets SNP variants were renamed so that AA represented the most common homozygote, and BB the least common homozygote.

@@

\subsection{Software}
\label{sec:software}
Data handling, editing and preparation, summary of results and plots were all performed using the open-source environment for statistical programming R \cite{r_core_team_r:_2014}. All imputation methods except Beagle and FILLIN were implemented in R: MNI directly in base R; KNNI using the function \emph{knncatimpute()} from the Scrime package \cite{schwender_scrime:_2013}; SVDI with the R package ``bcv'' \cite{perry_bcv:_2009}; RFI using the ``MissForest'' \cite{stekhoven_missforestnon-parametric_2012} R package (with parameters: ntree=100, maxiter=10, parallelize='variables'). The ``Beagle'' localized haplotype clustering imputation method was implemented with the Beagle software version 3.3.2 \cite{browning_rapid_2007}. The FILLIN algorithm is implemented using the Tassel CLI plugin \emph{-FILLINFindHaplotypesPlugin} followed by \emph{-FILLINImputationPlugin}. The latter allowed accuracy measurements through \emph{-accuracy} and \emph{-propSitesMask} options.\\
The Bowtie 2 tool \cite{langmead_fast_2012} was used to query the consensus sequence of each alfalfa tag pair containing a SNP against the \emph{M. truncatula} reference genome Version 4.0 using the \emph{-verysensitivelocal} preset.
\textcolor{red}{TO BE WRITTEN: what about Rice alignment, what sw was used? How many marker did align? We need to report stats for alfalfa, too? (about half of the marker aligned).}

>>>>

In rice, DNA was isolated from three-weeks old leaves using the DNeasy Plant Mini Kit (QIAGEN) with a TECAN Freedom EVO150 liquid handling robot (TECAN Group Ltd, Switzerland). DNA digestion was performed on 100 ng samples in 96-well plates using ApeKI, which was shown to cut every 1 kb on average in a in-silico digestion of the Nipponbare reference genome, and 96-plex libraries constructed according to the GBS protocol. The libraries were loaded into Genome Analyzer II (Illumina, Inc., San Diego, CA) for sequencing. Raw sequence data filtering, sequence alignment to the rice reference genome (Os-Nipponbare-Reference-IRGSP-1.0, \cite{kawahara_improvement_2013}), and SNP calling from GBS genotyping were carried out using the Tassel GBS pipeline \cite{glaubitz_tassel-gbs:_2014}.\\
In total, 32\,706, 40\,734 and 166\,418 SNP markers were called by GBS in Alfalfa-PV, Alfalfa-Med and Rice, respectively (see Table~\ref{tab:descriptive_statistics}). In all datasets SNP variants were renamed so that AA represented the most common homozygote, and BB the least common homozygote.

@@

\subsection{Software}
\label{sec:software}
Data handling, editing and preparation, summary of results and plots were all performed using the open-source environment for statistical programming R \cite{r_core_team_r:_2014}. All imputation methods except Beagle and FILLIN were implemented in R: MNI directly in base R; KNNI using the function \emph{knncatimpute()} from the Scrime package \cite{schwender_scrime:_2013}; SVDI with the R package ``bcv'' \cite{perry_bcv:_2009}; RFI using the ``MissForest'' \cite{stekhoven_missforestnon-parametric_2012} R package (with parameters: ntree=100, maxiter=10, parallelize='variables'). The ``Beagle'' localized haplotype clustering imputation method was implemented with the Beagle software version 3.3.2 \cite{browning_rapid_2007}. The FILLIN algorithm is implemented using the Tassel CLI plugin \emph{-FILLINFindHaplotypesPlugin} followed by \emph{-FILLINImputationPlugin}. The latter allowed accuracy measurements through \emph{-accuracy} and \emph{-propSitesMask} options.\\
The Bowtie 2 tool \cite{langmead_fast_2012} was used to query the consensus sequence of each alfalfa tag pair containing a SNP against the \emph{M. truncatula} reference genome Version 4.0 using the \emph{-verysensitivelocal} preset. The BWA alignment tool \cite{li2009fast} was used to align rice tags on Rice Genome Annotation Project Release 7.
